### 2022-04-25 input/appendices.tex
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok
minors

\section{Table of notations}

@@

    $G$ & \underline{G}raph    & Represents a network.\\
    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\
    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\

@@

    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
    $D_x$ & \underline{d}elivered & Set of delivered messages by \Process $x$.\\

>>>>

\section{Table of notations}
\label{appendix:notations}

@@

    $G$ & \underline{G}raph    & Represents a network.\\
    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\

@@

    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
    $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\

### 2022-04-25 input/conclusion.tex
minors

As future work, we plan to evaluate our proposal within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem (IPFS)~\cite{ipfs}. This would
assess the relevance of \NAME in real systems subject to high
dynamicity, and compare it against its current DHT-based indexing
system that does not include distance in its operation. More
generally, we claim that \NAME and its extension can constitute
novel building blocks for geo-distributed services.  For instance,
\NAME could complement content delivery infrastructures by efficiently
sharing between \processes attached to the same CDN server the
locations of web objects that have already been downloaded. This would
further improve the containment of web traffic in our networks, and in
turns, reduce the overall traffic footprint.

>>>>

As future work, we plan to evaluate our proposal within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem (IPFS)~\cite{ipfs}. This would
assess the relevance of \NAME in real systems subject to high
dynamicity, and compare it against its current DHT-based indexing
system that does not include distance in its operation. More
generally, we claim that \NAME and its extension can constitute novel
building blocks for geo-distributed services.  For instance, \NAME
could complement content delivery
infrastructures~\cite{triukose2011measuring} by efficiently sharing
between \processes attached to the same CDN server the locations of
web objects that have already been downloaded. This would further
improve the containment of web traffic in our networks, and in turns,
reduce the overall traffic footprint.
